\input{preamble}
\begin{document}
\input{sections/header}
\titleline{Senior Fullstack Software Engineer \textbar{} AI-Native Healthcare Platforms, Backend Systems, and Product Automation}
\rsection{Summary}
Software engineer focused on AI-native product platforms, backend services, APIs, data workflows, and operationally sensitive systems. Former Meta and Google engineer with deep Python and Java experience, strong AI-assisted TypeScript capability, and a track record of shipping reliable systems across healthcare, regulated cloud, commerce, identity, and agent-infrastructure domains. Built early Gemini-based software-engineering agents, SWE-bench-style evaluation harnesses, and a live autonomous-agent fleet with observability, CI gates, and human-review controls.
\rsection{Alpaca Health Alignment}
\begin{itemize}
  \item Built healthcare, regulated cloud, identity, and commerce systems where data integrity, sensitive workflows, and operational reliability matter, including Lumeris, ClearDATA, Citi, Google, and Meta.
  \item Owns systems end-to-end across product requirements, backend data models, APIs, reliability, instrumentation, testing, and user-impact measurement rather than narrow feature slices.
  \item Strong fit for AI-native clinical and operational workflows: production agent systems, retrieval and tool use, memory/context handling, evals, guardrails, and workflow automation with human-review boundaries.
  \item Product-platform background maps well to scheduling, billing, payroll, credentialing, compliance, parent/provider communication, and internal automation systems that turn messy real-world workflows into software abstractions.
\end{itemize}
\rsection{Selected Product, Healthcare \& AI Systems Portfolio}
\subsec{Healthcare, Regulated Systems \& Product Platforms}
\begin{itemize}
  \item Built backend, platform, cloud, and healthcare systems in Python and Java across APIs, data workflows, and regulated environments at Lumeris, ClearDATA, Citi, Google, and Meta.
  \item Built trust-sensitive systems for internal security, enterprise identity, access management, and credential boundaries, with emphasis on privacy, reliability, and controlled access to sensitive workflows.
  \item At Meta Marketplace, expanded third-party partner APIs and shipped-listing workflows, then launched an ML-assisted listing flow that removed manual item-weight entry, met launch-quality thresholds, and lifted new-listing creation about 8\%.
\end{itemize}
\subsec{AI-Native Engineering, Tooling \& Fullstack Execution}
\begin{itemize}
  \item In Google Cloud Office of the CTO, built early Gemini-based software-engineering agents, SWE-bench evaluation harnesses, planning-vs-execution metrics, and vector-search benchmarks.
  \item Runs a live autonomous-agent fleet with MCP-style tools, reusable skills, OpenTelemetry traces and metrics, CI-backed quality gates, and recovery loops for long-running credentialed workflows.
  \item Uses AI-assisted engineering workflows while preserving review, testing, and human-control boundaries; strongest implementation depth is Python/Java with AI-assisted TypeScript delivery.
\end{itemize}
\input{sections/experience}
\input{sections/publicwork}
\input{sections/skills}
\end{document}
