\input{preamble}
\begin{document}
\input{sections/header}
\titleline{Forward Deployment Engineer \textbar{} Agentic AI Control Planes, Integrations, and Observability}
\rsection{Summary}
Software engineer focused on production agentic AI systems, forward-deployed integration work, secure tool runtimes, and observable distributed platforms. Former Meta and Google engineer who built early Gemini-based software-engineering agents, SWE-bench-style eval harnesses, vector-search benchmarks, and customer-facing platform systems. Runs a live autonomous-agent fleet with MCP-style tools, skills, observability, CI gates, human-review thresholds, and credentialed workflows.
\rsection{Selected Agentic AI Deployment Portfolio}
\subsec{Agent Control Planes, Integrations \& Governance}
\begin{itemize}
  \item Built a production multi-agent runtime where MCP servers expose callable capabilities and skills encode reusable procedures, with broker-held credentials, security-audit gates, and human-review thresholds.
  \item Designed recoverable orchestration loops, tool-use contracts, and dispatch/fan-out patterns for six always-on agents executing real workflows across documents, CI repair, repo changes, and long-running task decomposition.
  \item Built CI-backed verification and evaluation loops for autonomous engineering work, including SWE-bench-style harnesses, planning-vs-execution metrics, multi-substrate testing, and runner reliability checks.
\end{itemize}
\subsec{Observability, Security \& Enterprise Runtime Fit}
\begin{itemize}
  \item Instrumented agent fleets with OpenTelemetry traces, metrics, and logs across tool calls, token use, latency, trajectories, and recovery behavior, with live dashboards for operating long-running workflows.
  \item Modeled each agent as a reusable infrastructure module for identity, runtime, skills, schedules, and secrets, using GitOps and IaC patterns instead of one-off deployment work.
  \item Built trust-sensitive systems across internal security, enterprise identity, access management, and regulated healthcare/cloud environments.
\end{itemize}
\input{sections/experience}
\input{sections/publicwork}
\input{sections/skills}
\end{document}
