\input{preamble}
\begin{document}
\input{sections/header}
\titleline{Senior AI Software Engineer \textbar{} Enterprise AI, Python Backend Systems, and Financial Platforms}
\rsection{Summary}
Senior software engineer focused on enterprise AI applications, Python backend systems, agentic workflows, and reliable software platforms for regulated environments. Former Meta and Google engineer with experience across financial, healthcare, cloud, and commerce systems, including Citi, Google Cloud Office of the CTO, Meta, ClearDATA, and Lumeris. Builds practical AI-enabled software that integrates with existing platforms, data workflows, APIs, access controls, and production operations.
\rsection{Selected Enterprise AI \& Backend Platform Portfolio}
\subsec{Enterprise AI Applications, Agents \& Developer Productivity}
\begin{itemize}
  \item In Google Cloud Office of the CTO, built Gemini-based software-engineering agents, SWE-bench evaluation harnesses, planning-vs-execution metrics, and vector-search benchmarks.
  \item Runs a live autonomous-agent fleet with MCP-style callable tools, reusable skills, CI-backed verification, traceable execution, scheduling, messaging, credential boundaries, and human-review controls.
  \item Designs AI-enabled backend workflows where agents and applications call APIs, documents, browser actions, and external systems through typed interfaces, with retries, recovery, and operational guardrails.
\end{itemize}
\subsec{Python Backend Systems, Financial Context \& Existing Platforms}
\begin{itemize}
  \item Built backend, cloud, and regulated systems across Citi, Google, Meta, ClearDATA, and Lumeris, with emphasis on privacy, access control, reliability, maintainable APIs, and production tradeoffs.
  \item Strongest implementation depth is Python and Java, with AI-assisted TypeScript delivery and experience modernizing product-platform services, developer tooling, and data-intensive workflows.
  \item At Meta Marketplace, expanded third-party partner APIs and shipped-listing workflows for partner and seller-facing commerce systems, then launched an ML-assisted listing flow that lifted new-listing creation about 8\%.
\end{itemize}
\input{sections/experience}
\input{sections/publicwork}
\input{sections/skills}
\end{document}
