\input{preamble}
\begin{document}
\input{sections/header}
\titleline{Tech Lead, Full Stack \textbar{} Agent-Driven SDLC, Product Engineering, Backend Platforms, and Reliability}

\rsection{Summary}
Senior software engineer and technical lead for product-facing backend and platform systems, with experience across Meta, Google, Citi, ClearDATA, and Lumeris. Built agent-driven software-engineering systems in Google Cloud Office of the CTO, including Gemini-based coding agents, SWE-bench evaluation harnesses, planning-vs-execution metrics, and vector-search benchmarks. Runs a live autonomous-agent fleet with callable tools, reusable skills, CI-backed verification, scheduling, messaging, credential boundaries, observability, and human-review controls. Strongest depth in Python and Java, practical JavaScript/TypeScript and React capability, and a track record of taking ambiguous systems from 1 to broader adoption without overstating stack-specific experience.

\rsection{Selected Fit for Attention}
\subsec{Agent-Driven SDLC and Engineering Leverage}
\begin{itemize}
  \item Built Gemini-based software-engineering agents and SWE-bench evaluation harnesses in Google Cloud Office of the CTO, using metrics to separate planning quality, execution quality, and end-to-end task success.
  \item Operates a live multi-agent development and operations fleet where agents triage work, call tools, edit code, run tests, verify artifacts, update durable skills, and escalate irreversible actions to a human owner.
  \item Designs agent workflows around typed tool boundaries, source-grounded context, approval gates, traceable execution, retries, recovery paths, and evidence-backed completion instead of unchecked automation.
\end{itemize}

\subsec{Technical Leadership, Product Ownership, and 1 to N Scaling}
\begin{itemize}
  \item Led ambiguous work from problem framing through architecture, implementation, launch evidence, and long-term maintainability across consumer, commerce, identity, cloud, and healthcare systems.
  \item At Meta Marketplace, expanded third-party partner APIs and shipped-listing workflows, then launched an ML-assisted listing flow that met launch-quality accuracy and lifted new-listing creation about 8\%.
  \item At Google Play, helped build \href{https://support.google.com/googleplay/answer/16561562}{Play Games Leagues} from the ground up on a five-engineer team, balancing user-facing product quality with backend platform requirements.
  \item Partners closely with product, design, leadership, and customers, using product judgment, metrics, and system tradeoffs to decide what to build and how to sequence it.
\end{itemize}

\subsec{Backend, Platform, Reliability, and Full-Stack Execution}
\begin{itemize}
  \item Built production backend services, APIs, data workflows, identity systems, and platform tooling in Python, Java, Kotlin, SQL, and related JVM/server-side stacks.
  \item Uses Kubernetes, Docker, Linux, GitHub Actions, Actions Runner Controller, CI/CD, logs, metrics, traces, and operational gates to make platform and agent systems observable and recoverable.
  \item Practical with React and TypeScript for product surfaces and AI-assisted full-stack delivery, while strongest implementation depth remains backend, platform, agents, and reliability.
  \item Learns unfamiliar production stacks quickly through source-driven implementation, tests, instrumentation, and small verified releases rather than claiming prior ownership of every technology in a target stack.
\end{itemize}

\rsection{Experience}
\role{Meta}{Software Engineer}{New York, NY \textbar{} 2025 to 2026}
\begin{itemize}
  \item Expanded Facebook Marketplace third-party partner APIs and shipped-listing workflows for partner and seller-facing commerce.
  \item Shipped an ML-assisted listing flow that removed manual item-weight entry for shipped listings; predictions were evaluated against user-entered weights and carrier actuals, met the launch threshold near 80\% accuracy, and lifted new-listing creation about 8\%.
  \item Worked in a large-scale product organization where reliability, product quality, experimentation, review quality, and operational ownership shaped delivery.
\end{itemize}

\role{Google}{Software Engineer}{Pittsburgh / Austin / Remote / Atlanta \textbar{} 2018 to 2025}
\begin{itemize}
  \item Worked across Google Shopping Engineering Productivity, Google Play, Google Cloud Office of the CTO, and Internal Identity and Access Management.
  \item In Google Cloud Office of the CTO, built early agentic-coding systems: a Gemini-based software-engineering agent, SWE-bench eval harnesses, and planning-vs-execution metrics that guided funding and staffing; benchmarked vector-search frameworks at scale to position GCP's AI competitively.
  \item In Google Play, helped build \href{https://support.google.com/googleplay/answer/16561562}{Play Games Leagues} from the ground up on a five-engineer team and designed a configurable fuzzer for third-party Play APIs.
  \item Built Insider Risk systems for internal security, enterprise identity, and trust-sensitive access.
\end{itemize}

\role{Earlier}{Backend / Platform / Healthcare Engineering}{Citi, Lumeris, ClearDATA, and others}
\begin{itemize}
  \item Built backend, platform, cloud, and healthcare systems in Python and Java across APIs, data workflows, and regulated environments.
\end{itemize}

\rsection{Public Work and Current Systems}
\begin{itemize}
  \item \href{https://github.com/selamy-labs/agent-skills}{selamy-labs/agent-skills}: reusable agent procedures and operating standards for delegated coding, review, verification, and recovery.
  \item \href{https://github.com/pselamy}{github.com/pselamy}: public engineering portfolio spanning agent infrastructure, evaluation harnesses, automation, and system design artifacts.
  \item \href{https://selamy.dev}{selamy.dev}: public writing and portfolio surface for agent operations, technical leadership, and production-oriented AI systems.
\end{itemize}

\rsection{Technical Skills}
{\renewcommand{\arraystretch}{1.22}%
\begin{tabularx}{\linewidth}{@{}>{\bfseries}l X@{}}
Languages: & Python, Java, Kotlin, JavaScript/TypeScript, Hack, PHP, Bash, SQL \\
AI / Agents: & AI agents, agent-driven SDLC, tool calling, MCP-style tools, skills/playbooks, SWE-bench, eval harnesses, context engineering, RAG, model routing, secure tool execution \\
Product \& Backend: & API design, backend services, data models, workflow orchestration, product metrics, experimentation, launch analysis, developer infrastructure \\
Frontend: & React, TypeScript, JavaScript, product UI collaboration, AI-assisted full-stack delivery \\
Reliability \& Platform: & Kubernetes, Docker, Linux, GitHub Actions, Actions Runner Controller, CI/CD, observability, traces, metrics, logs, incident-oriented verification, OpenTofu/Terraform, Argo CD \\
Security \& Enterprise: & internal IAM, auth boundaries, insider-risk systems, credential brokering, trust-sensitive workflows, privacy/security review gates \\
\end{tabularx}}
\end{document}
