\input{preamble}
\begin{document}
\input{sections/header}
\titleline{Senior Software Engineer \textbar{} AI Data Platforms, Full-Stack Systems, and Cloud Infrastructure}
\rsection{Summary}
Software engineer focused on AI platform systems, backend services, enterprise APIs, data workflows, and reliable cloud infrastructure. Former Meta and Google engineer with experience across product engineering, distributed systems, agent tooling, evaluation harnesses, and observable production services. Strongest depth is Python and Java, with TypeScript-capable full-stack delivery, AWS/cloud platform experience, and practical AI-agent systems running against real tools, repos, and external workflows.
\rsection{Selected AI Platform, Product \& Data Systems Portfolio}
\subsec{AI-Agent Platforms, Evals \& Tooling}
\begin{itemize}
  \item Built MCP-style capability layers where agents invoke tools, APIs, document workflows, browser actions, and external-system actions through typed, reusable interfaces.
  \item Designed multi-step agent orchestration with stateful task decomposition, retries, failure recovery, tool routing, scheduling, and credential boundaries for production workflows.
  \item In Google Cloud Office of the CTO, built Gemini-based software-engineering agents, SWE-bench evaluation harnesses, planning-vs-execution metrics, and vector-search benchmarks.
\end{itemize}
\subsec{Large-Scale Product, API \& Cloud Systems}
\begin{itemize}
  \item At Meta Marketplace, expanded third-party partner APIs and shipped-listing workflows for partner and seller-facing commerce systems.
  \item Shipped an ML-assisted listing flow that removed manual item-weight entry for shipped listings; evaluated predictions against user-entered weights and carrier actuals, met the launch threshold near 80\% accuracy, and lifted new-listing creation about 8\%.
  \item Built backend, cloud, healthcare, and regulated systems across Google, Meta, Citi, ClearDATA, and Lumeris, emphasizing reliable APIs, data workflows, access controls, and maintainable platform services.
\end{itemize}
\input{sections/experience}
\input{sections/publicwork}
\input{sections/skills}
\end{document}
