\input{preamble}
\begin{document}
\input{sections/header}
\titleline{Software Engineer, Core Infrastructure \textbar{} Browser Agents, Distributed Platforms, and Reliability}
\rsection{Summary}
Software engineer focused on production agent infrastructure, distributed platform systems, developer APIs, and reliable automation. Former Meta and Google engineer who built early Gemini-based software-engineering agents, SWE-bench-style evaluation harnesses, vector-search benchmarks, and product/platform systems. Runs a live autonomous-agent fleet with MCP-style tools, CI-backed verification, observability, recovery loops, and browser-capable workflows.
\rsection{Selected Infrastructure \& Browser-Agent Portfolio}
\subsec{Agent Runtime, APIs \& Platform Foundations}
\begin{itemize}
  \item Built a live multi-agent runtime with callable tools, reusable skills, browser actions, credentialed workflows, and orchestration patterns for long-running automation.
  \item Designed tool-use contracts, dispatch/fan-out patterns, and CI-backed verification loops for autonomous engineering work across repos, documents, and web/browser tasks.
  \item At Google Cloud Office of the CTO, built Gemini-based software-engineering agents, SWE-bench evaluation harnesses, and vector-search benchmarks for agentic coding workflows.
\end{itemize}
\subsec{Reliability, Operations \& Product Infrastructure}
\begin{itemize}
  \item Instrumented systems with traces, metrics, logs, failure-recovery signals, and quality gates so production behavior is inspectable and debuggable.
  \item Built backend and platform services across Google, Meta, Citi, ClearDATA, and Lumeris, with strong Python/Java depth and AI-assisted TypeScript capability.
  \item At Meta Marketplace, expanded third-party partner APIs and shipped-listing workflows, then launched an ML-assisted listing flow that improved new-listing creation about 8\%.
\end{itemize}
\input{sections/experience}
\input{sections/publicwork}
\input{sections/skills}
\end{document}
