\input{preamble}
\begin{document}
\input{sections/header}
\titleline{Senior Software Engineer \textbar{} Generative AI Product Development, Agentic Workflows, and Internal Platforms}
\rsection{Summary}
Senior software engineer focused on taking generative-AI products from ambiguous internal need to production workflow: agentic coding systems, tool-calling runtimes, evaluation harnesses, context engineering, retrieval, and developer-facing platforms. Former Meta and Google engineer with Google Cloud Office of the CTO experience building early Gemini-based software-engineering agents, SWE-bench-style eval harnesses, planning-versus-execution metrics, and vector-search benchmarks. Builds pragmatic internal AI applications with Python/Java depth, product judgment, security boundaries, adoption focus, and measurable workflow impact.
\rsection{Selected Generative AI Product Development Portfolio}
\subsec{Greenfield GAI Products \& Internal Workflow Automation}
\begin{itemize}
  \item Built Gemini-based software-engineering agents in Google Cloud Office of the CTO, including tool-use loops, SWE-bench-style evaluation, planning-vs-execution measurement, and vector-search benchmarking across ScaNN, FAISS, and pgvector.
  \item Runs a live autonomous-agent fleet that turns internal workflows into callable tools, reusable skills, review-gated actions, scheduled jobs, document operations, messaging workflows, and CI-backed verification.
  \item Designs AI systems around real user workflows: context gathering, tool contracts, retrieval, structured outputs, safe execution boundaries, human approval gates, and measurable task outcomes rather than demo-only chat experiences.
\end{itemize}
\subsec{Product Ownership, Adoption \& Regulated Enterprise Fit}
\begin{itemize}
  \item Shipped an ML-assisted Meta Marketplace listing flow that removed manual item-weight entry, met launch-quality accuracy near 80\%, and lifted new shipped-listing creation about 8\%.
  \item Built internal platform and trust-sensitive systems across Google Cloud Office of the CTO, Google Internal IAM, Citi, ClearDATA, Lumeris, and Meta, with emphasis on stakeholder collaboration, secure APIs, reliability, and adoption.
  \item Strongest implementation depth is Python and Java, with AI-assisted TypeScript delivery and a track record of translating ambiguous business/product needs into production engineering systems.
\end{itemize}
\input{sections/experience}
\input{sections/publicwork}
\input{sections/skills}
\end{document}
