\input{preamble}
\begin{document}
\input{sections/header}
\titleline{Lead Software Engineer \textbar{} Developer Productivity, Distributed Systems, Kubernetes, and App Engineering}
\rsection{Summary}
Lead software engineer focused on developer productivity platforms, resilient backend systems, infrastructure automation, and AI-enabled engineering workflows. Former Meta and Google engineer with experience building internal platforms across Google Cloud Office of the CTO, Google Internal IAM, Google Play, Citi, ClearDATA, Lumeris, and Meta Marketplace. Strong Python and Java depth, practical Kubernetes/Linux/cloud experience, and a bias for user-facing developer tools that improve delivery, reliability, and engineering effectiveness firmwide.
\rsection{Selected Application Engineering \& Infrastructure Portfolio}
\subsec{Developer Productivity Platforms \& Firmwide Engineering Effectiveness}
\begin{itemize}
  \item Built early Gemini-based software-engineering agents, SWE-bench-style evaluation harnesses, planning-vs-execution metrics, and vector-search benchmarks in Google Cloud Office of the CTO to improve engineering workflows and technical decision-making.
  \item Runs a live autonomous-agent fleet with MCP-style callable tools, reusable skills, CI-backed verification, traceable execution, credential boundaries, and approval gates for external actions.
  \item Designs developer-focused systems that combine APIs, context layers, workflow orchestration, observability, and safe automation so teams can move from idea to production with fewer manual handoffs.
\end{itemize}
\subsec{Distributed Systems, Kubernetes \& Enterprise Infrastructure}
\begin{itemize}
  \item Built backend, platform, cloud, and regulated systems across Meta, Google, Citi, ClearDATA, and Lumeris, with emphasis on privacy, access control, resilient APIs, maintainable services, and production tradeoffs.
  \item Applies Kubernetes, Docker, Linux, Terraform/OpenTofu, Argo CD, GitHub Actions, cloud infrastructure, and observability to platform systems where reliability and clear failure modes matter.
  \item Collaborates across product, security, business, and engineering stakeholders to turn open-ended infrastructure needs into concrete architecture, implementation plans, and production rollouts.
\end{itemize}
\input{sections/experience}
\input{sections/publicwork}
\input{sections/skills}
\end{document}
