\input{preamble}
\begin{document}
\input{sections/header}
\titleline{Member of Technical Staff \textbar{} Forward-Deployed AI Systems, Workflow Automation, and Product Platforms}
\rsection{Summary}
Senior software engineer focused on AI-enabled workflow automation, forward-deployed product engineering, backend platforms, and agentic systems. Former Meta and Google engineer with experience translating ambiguous business workflows into reliable software across commerce, cloud, identity, healthcare, and regulated backend environments. Built Gemini-based software-engineering agents, SWE-bench evaluation harnesses, vector-search benchmarks, and a live autonomous-agent fleet with tool use, reusable skills, observability, CI gates, credential boundaries, and human-review controls. Strongest implementation depth in Python and Java, with practical JavaScript/TypeScript, cloud, API, integration, and reliability experience.
\rsection{Eagle AEC Alignment}
\begin{itemize}
  \item Strong match for Eagle's forward-deployed mandate: learn real user workflows quickly, identify leverage points, and ship durable software that improves speed, quality, and operational throughput.
  \item Built systems at the boundary of product, operations, and engineering, including Meta Marketplace seller workflows, Google Cloud Office of the CTO prototypes, Google Play developer tooling, and regulated backend platforms.
  \item Agent and automation portfolio maps to Eagle's focus on proposal generation, opportunity intelligence, relationship mapping, document intelligence, knowledge retrieval, AI-assisted workflows, and reusable deployment playbooks.
  \item Communicates across engineering, business, legal, design, content design, ML, and leadership stakeholders while preserving execution clarity, adoption metrics, reliability, and human-control boundaries.
\end{itemize}
\rsection{Selected AI Workflow, Platform \& Deployment Portfolio}
\subsec{Forward-Deployed AI, Agents \& Workflow Automation}
\begin{itemize}
  \item In Google Cloud Office of the CTO, built Gemini-based software-engineering agents, SWE-bench evaluation harnesses, planning-vs-execution metrics, and vector-search benchmarks for applied AI infrastructure decisions.
  \item Runs a live autonomous-agent fleet with MCP-style callable tools, reusable skills, scheduled workflows, messaging integrations, traceable execution, CI-backed verification, and recovery loops for long-running work.
  \item Designs AI-enabled workflows where agents and applications call APIs, documents, browser actions, and external systems through typed interfaces, with retries, auditability, and operational guardrails.
\end{itemize}
\subsec{Product Platforms, Integrations \& Real-World Operations}
\begin{itemize}
  \item At Meta Marketplace, expanded third-party partner APIs and shipped-listing workflows, then launched an ML-assisted listing flow that removed manual item-weight entry and lifted new-listing creation about 8\%.
  \item Built backend, cloud, identity, healthcare, financial, and commerce systems across Google, Meta, Citi, ClearDATA, and Lumeris, emphasizing APIs, data workflows, access control, reliability, and production tradeoffs.
  \item Instruments platform and agent systems with traces, metrics, logs, latency/error tracking, and operational gates so production behavior is visible and failures can be corrected.
\end{itemize}
\input{sections/experience}
\input{sections/publicwork}
\input{sections/skills}
\end{document}
