\input{preamble}
\begin{document}
\input{sections/header}
\titleline{Staff AI Platform Engineer \textbar{} AI-Native Engineering, Evals, and Private-Credit Data Systems}
\rsection{Summary}
Software engineer focused on AI-native engineering infrastructure, agent harnesses, evaluation systems, observability, backend platforms, and regulated data workflows. Former Meta and Google engineer with deep Python and Java backend depth, TypeScript-capable full-stack delivery, and hands-on agent tooling. Strong fit for Ellis's Staff AI Platform / Agent Infrastructure and Founding AI-Native Product Engineer tracks: building the harness, skills, evals, CI gates, audit trails, and data-boundary discipline that let AI agents ship trusted production software.
\rsection{Selected AI-Native Engineering, Evals \& Data Platform Portfolio}
\subsec{Agent Harnesses, Evals \& Observable Engineering}
\begin{itemize}
  \item Runs a live autonomous-agent fleet with MCP-style tools, reusable skills, workflow routing, tracing, CI gates, human-review controls, and operational recovery across real repositories and external workflows.
  \item In Google Cloud Office of the CTO, built Gemini-based software-engineering agents, SWE-bench evaluation harnesses, planning-vs-execution metrics, and vector-search benchmarks including ScaNN, FAISS, and pgvector.
  \item Built repeatable agent workflows around prompt/skill libraries, review loops, behavioral tests, failure recovery, and verification gates so agent-generated work can be inspected before it reaches production.
\end{itemize}
\subsec{Private-Credit Data-Layer Fit, Controls \& Product Systems}
\begin{itemize}
  \item Built backend, platform, cloud, and healthcare systems in Python and Java across APIs, data workflows, and regulated environments where correctness, access control, and auditability mattered.
  \item Built Insider Risk systems at Google for internal security, enterprise identity, trust-sensitive access, and reassignment of Drive items after employee exits.
  \item Built product and platform systems where data quality, API reliability, provenance, and operational correctness mattered directly, including Google Play API infrastructure and Meta Marketplace shipped-listing workflows.
\end{itemize}
\input{sections/experience}
\input{sections/publicwork}
\input{sections/skills}
\end{document}
