\input{preamble}
\begin{document}
\input{sections/header}
\titleline{Senior Software Engineer \textbar{} Full-Stack Product Systems, Real-Time Platforms, and AI Workflows}
\rsection{Summary}
Software engineer focused on scalable product platforms, backend services, APIs, real-time operations, and AI-enabled internal workflows. Former Meta and Google engineer with experience across Python, Java, cloud infrastructure, product engineering, evaluation harnesses, and reliable distributed systems. Built marketplace APIs and shipped-listing workflows at Meta, product and platform systems at Google, and a live autonomous-agent fleet with observability, CI gates, and operational recovery.
\rsection{Selected Product, Platform \& AI Systems Portfolio}
\subsec{Marketplace, Logistics-Adjacent Product Systems}
\begin{itemize}
  \item At Meta Marketplace, expanded third-party partner APIs and shipped-listing workflows for partner and seller-facing commerce.
  \item Shipped an ML-assisted listing flow that removed manual item-weight entry for shipped listings; evaluated predictions against user-entered weights and carrier actuals, met the launch threshold near 80\% accuracy, and lifted new-listing creation about 8\%.
  \item Built Google Play and commerce-adjacent product systems, including configurable API fuzzing and launch-quality engineering on a small product team.
\end{itemize}
\subsec{Reliability, Testing \& AI-Enabled Engineering}
\begin{itemize}
  \item Built CI-backed verification loops, automated evaluation harnesses, runner reliability checks, and quality gates for autonomous engineering workflows.
  \item Instrumented production agent systems with OpenTelemetry traces, metrics, logs, and dashboards across tool calls, latency, trajectories, and recovery behavior.
  \item Built backend, platform, cloud, healthcare, and regulated systems in Python and Java across APIs, data workflows, and operational environments.
\end{itemize}
\input{sections/experience}
\input{sections/publicwork}
\input{sections/skills}
\end{document}
