\input{preamble}
\begin{document}
\input{sections/header}
\titleline{VP, AI Engineer \textbar{} Agentic AI Platforms, Internal AI Products, and Investment Research Systems}
\rsection{Summary}
Senior software engineer focused on production AI systems, agentic platforms, internal AI products, retrieval, evaluation harnesses, and observable backend services for high-trust enterprise environments. Former Meta and Google engineer with Google Cloud Office of the CTO experience building early Gemini-based software-engineering agents, SWE-bench-style evaluation, planning-vs-execution metrics, and vector-search benchmarks. Builds pragmatic AI platforms that connect models, tools, data, and product workflows with clear guardrails, production telemetry, and measurable business outcomes.
\rsection{Selected Hudson Bay Capital Fit}
\subsec{Agentic AI Platforms \& Internal AI Products}
\begin{itemize}
  \item Built Gemini-based software-engineering agents in Google Cloud Office of the CTO, including tool-use loops, SWE-bench-style evaluation, planning-vs-execution measurement, and vector-search benchmarking across ScaNN, FAISS, and pgvector.
  \item Runs a live autonomous-agent fleet with MCP-style callable tools, reusable skills, scheduled jobs, document operations, messaging workflows, human approval gates, credential boundaries, and CI-backed verification.
  \item Designs AI systems around real internal workflows: context gathering, tool contracts, retrieval, structured outputs, safe execution boundaries, failure recovery, and measurable task outcomes rather than demo-only chat surfaces.
\end{itemize}
\subsec{Financial, Research \& High-Trust Platform Fit}
\begin{itemize}
  \item Built backend, platform, cloud, and regulated systems across Citi, Google, Meta, ClearDATA, and Lumeris, with emphasis on privacy, access control, reliability, maintainable APIs, and production tradeoffs.
  \item Shipped an ML-assisted Meta Marketplace listing flow that removed manual item-weight entry, met launch-quality accuracy near 80\%, and lifted new shipped-listing creation about 8\% through shadow-mode validation and staged rollout.
  \item Built a Python public-work artifact for investment-research-adjacent signal discovery that flags suspicious wallet activity on Polymarket prediction markets, complementing broader agentic AI and platform systems work.
\end{itemize}
\input{sections/experience}
\input{sections/publicwork}
\input{sections/skills}
\end{document}
