\input{preamble}
\begin{document}
\input{sections/header}
\titleline{Senior Software Engineer \textbar{} Production AI, Backend Platforms, and Financial Systems}
\rsection{Summary}
Senior software engineer focused on production AI systems, backend APIs, agentic workflows, retrieval, and observable platform services. Former Meta and Google engineer with experience across regulated and high-scale environments, including Citi, Google Cloud Office of the CTO, Meta, ClearDATA, and Lumeris. Builds pragmatic AI systems that move beyond demos: Python/Java backend services, LLM tool use, evaluation harnesses, monitoring, reliability controls, and clear collaboration with business and product stakeholders.
\rsection{Selected Production AI \& Financial Platform Portfolio}
\subsec{Production AI Systems, Retrieval \& Backend APIs}
\begin{itemize}
  \item Built Gemini-based software-engineering agents, SWE-bench-style evaluation harnesses, planning-vs-execution metrics, and vector-search benchmarks in Google Cloud Office of the CTO.
  \item Runs a live autonomous-agent fleet with MCP-style callable tools, reusable skills, CI-backed verification, traceable execution, credential boundaries, and human-review controls.
  \item Designs backend workflows where agents call APIs, documents, browser actions, and external systems through typed interfaces, with retries, failure recovery, scheduling, and operational guardrails.
\end{itemize}
\subsec{Financial, Regulated \& Enterprise Platform Fit}
\begin{itemize}
  \item Built backend, cloud, and regulated systems across Citi, Google, Meta, ClearDATA, and Lumeris, with emphasis on privacy, access control, reliability, maintainable APIs, and production tradeoffs.
  \item Strongest implementation depth is Python and Java, with AI-assisted TypeScript delivery and experience building product-platform services, developer tooling, and data-intensive workflows.
  \item Instrumented agent and platform systems with traces, metrics, logs, latency/error tracking, and CI gates so production behavior is visible and failures are recoverable.
\end{itemize}
\input{sections/experience}
\input{sections/publicwork}
\input{sections/skills}
\end{document}
