\input{preamble}
\begin{document}
\input{sections/header}
\titleline{Founding Product Infrastructure Engineer \textbar{} Agent Infrastructure, CI/CD, and Observability}
\rsection{Summary}
Software engineer focused on production agent infrastructure, reliable platform foundations, CI/CD gates, observability, and product-minded backend systems. Former Meta and Google engineer who built early Gemini-based software-engineering agents, SWE-bench-style evaluation harnesses, vector-search benchmarks, and production platform systems. Runs a live autonomous-agent fleet with MCP-style tools, reusable skills, traces, metrics, recovery loops, and controlled credentials.
\rsection{Selected Product Infrastructure Portfolio}
\subsec{Agent Infrastructure, Deployment \& Operational Hygiene}
\begin{itemize}
  \item Built infrastructure for always-on agents executing real workflows, including schedules, secrets, tool routing, workflow recovery, and human-review thresholds.
  \item Designed CI-backed quality gates, runner reliability checks, evaluation harnesses, and dispatch/fan-out patterns for multi-agent coding and document workflows.
  \item Modeled agents as reusable infrastructure modules for identity, runtime, tools, schedules, and state, using declarative patterns instead of one-off operations.
\end{itemize}
\subsec{Databases, APIs, Observability \& Scale Fit}
\begin{itemize}
  \item Built backend and platform services across Google, Meta, Citi, ClearDATA, and Lumeris, with strong Python/Java depth and cloud-production experience.
  \item Instrumented systems with OpenTelemetry traces, metrics, logs, latency/cost signals, and recovery behavior for inspectable production operations.
  \item Built partner APIs and product-platform workflows at Meta Marketplace, plus regulated healthcare/cloud and identity systems requiring reliability and secure access patterns.
\end{itemize}
\input{sections/experience}
\input{sections/publicwork}
\input{sections/skills}
\end{document}
