\input{preamble}
\begin{document}
\input{sections/header}
\titleline{Senior Software Engineer \textbar{} AI Developer Platform, Agent Context, DevEx, and Guardrailed Automation}
\rsection{Summary}
Senior software engineer focused on AI developer platforms that make agent-assisted engineering practical, secure, measurable, and effective at scale. Former Meta and Google engineer with hands-on experience building agentic coding systems, evaluation harnesses, context/retrieval layers, internal developer workflows, and production backend platforms. Runs a live autonomous-agent fleet using callable tools, reusable skills, CI-backed verification, human approval gates, observability, and secure credential boundaries.
\rsection{Selected AI Developer Platform Portfolio}
\subsec{Agent Context Layers, Workflows \& Guardrails}
\begin{itemize}
  \item Built Gemini-based software-engineering agents in Google Cloud Office of the CTO with SWE-bench-style eval harnesses, planning-vs-execution metrics, and vector-search benchmarks to improve model/tool selection and agent behavior.
  \item Runs an autonomous-agent platform that connects agents to source code, docs, calendars, Gmail, LinkedIn, files, GitHub, CI, browser actions, and structured tools through explicit contracts and review-gated workflows.
  \item Designs reusable agent skills, prompt/procedure libraries, tool interfaces, state management, retries, failure recovery, and observability so agents can safely investigate, modify, verify, and report work.
\end{itemize}
\subsec{Developer Experience, Measurement \& Production Adoption}
\begin{itemize}
  \item Built developer and product-platform systems across Google, Meta, Citi, ClearDATA, and Lumeris, including secure APIs, workflow systems, launch analysis, trust-sensitive access controls, and large-scale testing/fuzzing.
  \item Shipped an ML-assisted Meta Marketplace listing flow that met launch-quality accuracy near 80\% and lifted new shipped-listing creation about 8\%, demonstrating production ML-to-product impact.
  \item Instruments agent and platform workflows with traces, metrics, logs, latency/error tracking, CI gates, and human-review thresholds so engineering impact can be measured rather than assumed.
\end{itemize}
\input{sections/experience}
\input{sections/publicwork}
\input{sections/skills}
\end{document}
