\input{preamble}
\begin{document}
\input{sections/header}
\titleline{Senior Software Engineer \textbar{} Customer Intelligence, Data Enrichment, and AI Platforms}
\rsection{Summary}
Senior software engineer focused on customer-intelligence platforms, commerce workflows, backend infrastructure, and AI-enabled data systems. Former Meta and Google engineer with experience across Marketplace shipped-listing systems, partner APIs, product experimentation, enterprise data provenance, internal IAM, vector-search benchmarks, and AI-assisted software-engineering agents. Strong fit for OuterSignal's order-enrichment and identity/data-signal platform: APIs, data pipelines, privacy-aware enrichment, RAG/vector search, product dashboards, and early-stage ownership across backend, infrastructure, and product surfaces.
\rsection{Selected Commerce, Data \& AI Platform Portfolio}
\subsec{Commerce, Customer Signals \& Product Workflows}
\begin{itemize}
  \item At Meta Marketplace, expanded third-party partner APIs and shipped-listing workflows for partner and seller-facing commerce.
  \item Shipped an ML-assisted listing flow that removed manual item-weight entry for shipped listings; evaluated predictions against user-entered weights and carrier actuals, met the launch threshold near 80\% accuracy, and lifted new-listing creation about 8\%.
  \item Built product-growth systems across Facebook Marketplace, Facebook Dating, Google Play, and Google Shopping where user engagement, data quality, API reliability, and fast product iteration mattered directly.
\end{itemize}
\subsec{AI Data Infrastructure, Retrieval \& Operational Ownership}
\begin{itemize}
  \item In Google Cloud Office of the CTO, benchmarked vector-search frameworks including ScaNN, FAISS, and pgvector, and built Gemini-based software-engineering agents with SWE-bench evaluation harnesses.
  \item Built systems that aggregate context across documents, tasks, diffs, and code into shared knowledge surfaces, reducing duplicated work and improving operational visibility.
  \item Runs a live autonomous-agent fleet with MCP-style tools, reusable skills, workflow routing, tracing, CI gates, human-review controls, and operational recovery.
  \item Built backend, platform, cloud, healthcare, and regulated systems in Python and Java, with AI-assisted TypeScript delivery and experience around APIs, data workflows, privacy, access controls, and reliable operations.
\end{itemize}
\input{sections/experience}
\input{sections/publicwork}
\input{sections/skills}
\end{document}
