\input{preamble}
\begin{document}
\input{sections/header}
\titleline{AI Engineer \textbar{} Production Agents, Data-Intensive Workflows, and Renewable-Infrastructure Automation}
\rsection{Summary}
Software engineer focused on production AI agents, backend platforms, data-intensive workflows, and reliable automation for high-ambiguity domains. Former Meta and Google engineer with Python and Java depth, SQL/data-workflow experience, cloud/platform background, evaluation harnesses, and production ownership. Strong fit for Paces's AI Engineer role: building agentic automation for siting, interconnection, and permitting workflows, partnering with domain experts, moving ambiguous product needs into shipped systems, and scaling observable infrastructure in a fast-moving Brooklyn team.
\rsection{Selected Paces-Relevant Portfolio}
\subsec{Production Agents, Evals \& Automation}
\begin{itemize}
  \item In Google Cloud Office of the CTO, built Gemini-based software-engineering agents, SWE-bench evaluation harnesses, planning-vs-execution metrics, and vector-search benchmarks including ScaNN, FAISS, and pgvector.
  \item Runs a live autonomous-agent fleet with MCP-style tools, reusable skills, workflow routing, tracing, CI gates, human-review controls, and operational recovery across real credentialed workflows.
  \item Built agent/tool systems where uncertain human workflow steps are turned into callable tools, reusable procedures, review gates, and measurable execution loops.
\end{itemize}
\subsec{Data-Intensive Product, Platform \& Operational Systems}
\begin{itemize}
  \item At Meta Marketplace, expanded third-party partner APIs and shipped-listing workflows for partner and seller-facing commerce.
  \item Shipped an ML-assisted listing flow that removed manual item-weight entry for shipped listings; evaluated predictions against user-entered weights and carrier actuals, met the launch threshold near 80\% accuracy, and lifted new-listing creation about 8\%.
  \item Built backend, platform, cloud, healthcare, and regulated systems in Python and Java across APIs, data workflows, identity/security boundaries, and operational environments.
\end{itemize}
\input{sections/experience}
\input{sections/publicwork}
\input{sections/skills}
\end{document}
