\input{preamble}
\begin{document}
\input{sections/header}
\titleline{Senior Platform Software Engineer \textbar{} Scalable Systems, CI/CD, Cloud Infrastructure, and Automation}
\rsection{Summary}
Senior platform software engineer focused on scalable backend systems, developer infrastructure, CI/CD automation, production observability, and reliable internal platforms. Former Meta and Google engineer with experience across high-scale product systems, Google Cloud Office of the CTO, Google Play engineering productivity, Internal IAM, Citi, ClearDATA, and Lumeris. Strong Python/Java depth, Linux/cloud/Kubernetes experience, and a track record of moving ambiguous engineering-platform problems from concept to production.
\rsection{Selected Platform Engineering Portfolio}
\subsec{Scalable Systems, Automation \& Production Operations}
\begin{itemize}
  \item Built backend and platform systems across Google, Meta, Citi, ClearDATA, and Lumeris, with emphasis on APIs, data workflows, regulated environments, secure access controls, reliability, and production supportability.
  \item Designed and operated autonomous engineering workflows with CI-backed verification, GitHub Actions, scheduled jobs, retries, watchdogs, structured logs, metrics, and clear escalation paths for failures.
  \item Applies Kubernetes, Docker, Linux, Terraform/OpenTofu, Argo CD, cloud infrastructure, PostgreSQL, Redis, Kafka, and observability to systems where performance, stability, and automation matter.
\end{itemize}
\subsec{Developer Productivity, Research/Engineering Enablement \& AI Tooling}
\begin{itemize}
  \item In Google Cloud Office of the CTO, built Gemini-based software-engineering agents, SWE-bench-style eval harnesses, planning-vs-execution metrics, and vector-search benchmarks to support emerging AI engineering workflows.
  \item In Google Play, helped build Play Games Leagues on a five-engineer team and designed configurable fuzzing for third-party Play APIs, supporting API reliability and developer-facing launch quality.
  \item Runs a live agent platform with MCP-style tools, reusable skills, secure runtime boundaries, context retrieval, and human-review controls for software and operations workflows.
\end{itemize}
\input{sections/experience}
\input{sections/publicwork}
\input{sections/skills}
\end{document}
