\input{preamble}
\begin{document}
\input{sections/header}
\titleline{Forward Deployed Engineer \textbar{} Enterprise Agentic AI, Workflow Automation, and Deployment}
\rsection{Summary}
Software engineer focused on forward-deployed agentic AI systems, customer-facing workflow automation, production integrations, and observable deployment loops. Former Meta and Google engineer who built early Gemini-based software-engineering agents, SWE-bench-style eval harnesses, vector-search benchmarks, and trust-sensitive platform systems. Runs a live autonomous-agent fleet with MCP-style tools, reusable skills, CI gates, human-review thresholds, and long-running credentialed workflows.
\rsection{Selected Forward-Deployed AI Portfolio}
\subsec{Customer Workflows, Tools \& Agent Deployment}
\begin{itemize}
  \item Built reusable tool and skill layers where agents call APIs, manipulate documents, use browser actions, and execute multi-step workflows behind review and credential boundaries.
  \item Designed recoverable orchestration loops with state management, retries, failure handling, and human-review checkpoints for high-agency agent workflows.
  \item Built Gemini-based coding agents and SWE-bench-style evaluation harnesses in Google Cloud Office of the CTO, translating ambiguous agent behavior into measurable execution loops.
\end{itemize}
\subsec{Enterprise Readiness, Communication \& Production Ownership}
\begin{itemize}
  \item Built trust-sensitive systems across internal security, enterprise identity, access management, healthcare/cloud, and consumer commerce domains.
  \item Instrumented agent fleets with OpenTelemetry traces, metrics, logs, trajectory review, and CI gates to make autonomous behavior observable and accountable.
  \item Comfortable bridging product needs, technical discovery, platform tradeoffs, and fast implementation across Python, Java, cloud systems, and AI-assisted TypeScript.
\end{itemize}
\input{sections/experience}
\input{sections/publicwork}
\input{sections/skills}
\end{document}
