\input{preamble}
\begin{document}
\input{sections/header}
\titleline{Staff Backend Engineer \textbar{} Distributed Systems, Platform Infrastructure, and Production AI}
\rsection{Summary}
Staff backend engineer focused on distributed systems, platform infrastructure, production APIs, data workflows, and reliable cloud services. Former Meta and Google engineer with experience across high-scale product systems, regulated backend platforms, developer tooling, and AI-agent infrastructure. Strongest implementation depth is Python and Java, with TypeScript-capable delivery, AWS/cloud platform experience, and practical production ownership from design through deployment, observability, debugging, and iteration.
\rsection{Selected Backend, Infrastructure \& AI Platform Portfolio}
\subsec{Distributed Backend Systems, APIs \& Cloud Infrastructure}
\begin{itemize}
  \item Built backend, cloud, healthcare, and regulated systems across Google, Meta, Citi, ClearDATA, and Lumeris, emphasizing reliable APIs, access controls, data workflows, and maintainable platform services.
  \item At Meta Marketplace, expanded third-party partner APIs and shipped-listing workflows for partner and seller-facing commerce systems.
  \item Shipped an ML-assisted listing flow that removed manual item-weight entry for shipped listings; evaluated predictions against user-entered weights and carrier actuals, met the launch threshold near 80\% accuracy, and lifted new-listing creation about 8\%.
\end{itemize}
\subsec{Production AI, Agent Infrastructure \& Operational Reliability}
\begin{itemize}
  \item In Google Cloud Office of the CTO, built Gemini-based software-engineering agents, SWE-bench evaluation harnesses, planning-vs-execution metrics, and vector-search benchmarks.
  \item Designed multi-step agent orchestration with stateful task decomposition, retries, failure recovery, tool routing, scheduling, credential boundaries, and CI-backed verification for production workflows.
  \item Instrumented agent and platform systems with traces, metrics, logs, latency/error tracking, and operational gates so production behavior is visible and failures are recoverable.
\end{itemize}
\input{sections/experience}
\input{sections/publicwork}
\input{sections/skills}
\end{document}
