\input{preamble}
\begin{document}
\input{sections/header}
\titleline{Staff Software Engineer \textbar{} User Profile Systems, Distributed Backend Platforms, and Production AI}
\rsection{Summary}
Staff software engineer focused on high-scale backend systems, user/profile and commerce platforms, distributed services, and production AI-agent infrastructure. Former Meta and Google engineer with experience across marketplace product systems, identity and access-control platforms, regulated backend services, and Gemini-based software-engineering agents. Builds reliable, observable systems end to end, with strongest implementation depth in Python and Java plus AI-assisted TypeScript and Go-capable delivery.
\rsection{Selected Backend, Profile Systems \& AI Platform Portfolio}
\subsec{High-Scale Backend, User/Profile \& Commerce Systems}
\begin{itemize}
  \item At Meta Marketplace, expanded third-party partner APIs and shipped-listing workflows for partner and seller-facing commerce systems, with emphasis on product reliability, API design, and high-signal iteration.
  \item Shipped an ML-assisted listing flow that removed manual item-weight entry for shipped listings; evaluated predictions against user-entered weights and carrier actuals, met the launch threshold near 80\% accuracy, and lifted new-listing creation about 8\%.
  \item Built cloud, identity, healthcare, and regulated backend systems across Google, Citi, ClearDATA, and Lumeris, emphasizing access control, API reliability, data workflows, maintainability, and production tradeoffs.
\end{itemize}
\subsec{Production AI, Agent Infrastructure \& Operational Reliability}
\begin{itemize}
  \item In Google Cloud Office of the CTO, built Gemini-based software-engineering agents, SWE-bench evaluation harnesses, planning-vs-execution metrics, and vector-search benchmarks.
  \item Runs a live autonomous-agent fleet with MCP-style callable tools, reusable skills, CI-backed verification, traceable execution, scheduling, messaging, credential boundaries, and human-review controls.
  \item Instruments agent and platform systems with traces, metrics, logs, latency/error tracking, and operational gates so production behavior is visible and failures are recoverable.
\end{itemize}
\input{sections/experience}
\input{sections/publicwork}
\input{sections/skills}
\end{document}
