\input{preamble}
\begin{document}
\input{sections/header}
\titleline{Automation Engineer \textbar{} Agentic Orchestration, Enterprise AI Automation, and LLM Systems}
\rsection{Summary}
Senior software engineer focused on agentic orchestration, enterprise AI automation, LLM-backed workflows, and production software platforms. Former Meta and Google engineer with hands-on experience building Gemini-based software-engineering agents, SWE-bench evaluation harnesses, vector-search benchmarks, and a live autonomous-agent fleet with callable tools, reusable skills, scheduling, messaging, credential boundaries, and human-review controls. Strongest implementation depth in Python and Java, with practical API, integration, observability, and reliability experience across cloud, commerce, identity, healthcare, and regulated backend systems.
\rsection{Selected Agentic Orchestration \& Enterprise Automation Portfolio}
\subsec{Agentic Orchestration, LLM Systems \& Evaluation}
\begin{itemize}
  \item In Google Cloud Office of the CTO, built Gemini-based software-engineering agents, SWE-bench evaluation harnesses, planning-vs-execution metrics, and vector-search benchmarks.
  \item Runs a live autonomous-agent fleet with MCP-style callable tools, reusable skills, CI-backed verification, traceable execution, scheduling, messaging, credential boundaries, and human-review controls.
  \item Designs AI-enabled workflows where agents and applications call APIs, documents, browser actions, and external systems through typed interfaces, with retries, recovery, and operational guardrails.
\end{itemize}
\subsec{Enterprise Integration, Automation \& Production Reliability}
\begin{itemize}
  \item Built backend, cloud, identity, healthcare, financial, and commerce systems across Google, Meta, Citi, ClearDATA, and Lumeris, emphasizing access control, API reliability, data workflows, maintainability, and production tradeoffs.
  \item Instruments agent and platform systems with traces, metrics, logs, latency/error tracking, and operational gates so production behavior is visible and failures are recoverable.
  \item At Meta Marketplace, expanded third-party partner APIs and shipped-listing workflows, then launched an ML-assisted listing flow that lifted new-listing creation about 8\%.
\end{itemize}
\input{sections/experience}
\input{sections/publicwork}
\input{sections/skills}
\end{document}
