\input{preamble}
\begin{document}
\input{sections/header}
\titleline{Staff Software Engineer \textbar{} Robotics Infrastructure, Developer Tooling, and AI Agent Platforms}
\rsection{Summary}
Staff-level software engineer building infrastructure, developer tooling, backend platforms, and AI-agent systems for high-ambiguity product environments. Former Meta and Google engineer with experience across cloud infrastructure, internal developer platforms, API testing, production security systems, and commerce-scale ML workflows. Runs a live autonomous-agent fleet using Kubernetes-style isolated runtimes, Terraform/OpenTofu, CI-backed verification, OpenTelemetry, MCP-style callable capabilities, and reusable skills, directly aligned with robot deployment, telemetry, secure cloud communication, and developer velocity.
\rsection{Selected Robotics Platform, Infrastructure \& Agent Systems Portfolio}
\subsec{Infrastructure, Developer Tooling \& Reliability}
\begin{itemize}
  \item Built CI-backed verification loops, automated evaluation harnesses, runner reliability checks, and quality gates for autonomous engineering workflows.
  \item Instrumented production agent systems with OpenTelemetry traces, metrics, logs, and dashboards across tool calls, latency, trajectories, recovery behavior, and operational health.
  \item Modeled each agent as a reusable Terraform/OpenTofu module covering identity, runtime, skills, schedule, secrets, and operational configuration, turning fleet changes into declarative infrastructure updates.
  \item Built Google Play API test infrastructure, including a configurable fuzzer for third-party Play APIs, and earlier Google Shopping experimentation environments that let engineering and design teams test without production impact.
\end{itemize}
\subsec{Agentic AI, Backend Platforms \& Ambiguous Technical Programs}
\begin{itemize}
  \item Built a production multi-agent fleet on Nous Research's open-source Hermes with per-agent isolation, GitOps, CI gates, scheduling, messaging, browser and terminal tools, and controlled credentialed execution.
  \item In Google Cloud Office of the CTO, built early agentic-coding systems, SWE-bench evaluation harnesses, and planning-vs-execution metrics to de-risk emerging AI engineering workflows.
  \item At Meta Marketplace, shipped an ML-assisted listing flow that removed manual item-weight entry for shipped listings; predictions were evaluated against user-entered weights and carrier actuals, met the launch threshold near 80\% accuracy, and lifted new-listing creation about 8\%.
  \item Built backend, platform, cloud, healthcare, and regulated systems in Python and Java across APIs, data workflows, production engineering, and operational environments.
\end{itemize}
\input{sections/experience}
\input{sections/publicwork}
\input{sections/skills}
\end{document}
