\input{preamble}
\begin{document}
\input{sections/header}
\titleline{Forward Deployed Engineer \textbar{} Agentic Tooling, Enterprise AI Platforms, and Evals}
\rsection{Summary}
Software engineer focused on forward-deployed AI systems, agentic tooling, evaluation loops, and reusable platform infrastructure. Former Meta and Google engineer who built early Gemini-based software-engineering agents, SWE-bench-style eval harnesses, vector-search benchmarks, and production product/platform systems. Runs a live autonomous-agent fleet with MCP-style tools, reusable skills, observability, CI gates, and human-review controls.
\rsection{Selected Forward-Deployed AI and Agent Platform Portfolio}
\subsec{Agentic Tooling, Enterprise Workflows \& Customer-Facing Systems}
\begin{itemize}
  \item Built MCP-style capability layers where agents invoke tools, APIs, document workflows, browser actions, and external-system actions through typed, reusable interfaces.
  \item Designed multi-step agent orchestration with task decomposition, retries, failure recovery, tool routing, schedules, and credential boundaries for production workflows.
  \item Built marketplace, healthcare, cloud, and product-platform systems where reliability, privacy, access controls, and stakeholder coordination were central to delivery.
\end{itemize}
\subsec{Evaluation, Observability \& AI Infrastructure}
\begin{itemize}
  \item In Google Cloud Office of the CTO, built Gemini-based software-engineering agents, SWE-bench evaluation harnesses, planning-vs-execution metrics, and vector-search benchmarks.
  \item Instrumented agent fleets with OpenTelemetry traces, metrics, and logs across tool calls, latency, token use, trajectories, and recovery behavior.
  \item Built CI-backed verification loops, automated evaluation harnesses, runner reliability checks, and quality gates for autonomous engineering workflows.
\end{itemize}
\input{sections/experience}
\input{sections/publicwork}
\input{sections/skills}
\end{document}
