\input{preamble}
\begin{document}
\input{sections/header}
\titleline{Senior Software Engineer \textbar{} Vertical AI, Supply-Chain Workflows, and Platform Systems}
\rsection{Summary}
Software engineer focused on AI-enabled product workflows, backend platforms, operational systems, and applied agent infrastructure. Former Meta and Google engineer with experience across commerce/logistics-adjacent product systems, Python and Java services, cloud platforms, evaluation harnesses, and reliable distributed systems. Built shipped-listing and partner API workflows at Meta Marketplace, product/platform systems at Google, and a live autonomous-agent fleet with observability, CI gates, and operational recovery.
\rsection{Selected Vertical AI \& Supply-Chain-Relevant Portfolio}
\subsec{Commerce, Logistics \& Operational Workflow Systems}
\begin{itemize}
  \item At Meta Marketplace, expanded third-party partner APIs and shipped-listing workflows for partner and seller-facing commerce.
  \item Shipped an ML-assisted listing flow that removed manual item-weight entry for shipped listings; evaluated predictions against user-entered weights and carrier actuals, met the launch threshold near 80\% accuracy, and lifted new-listing creation about 8\%.
  \item Built Google Play and Google Shopping product/platform systems, including launch-quality API infrastructure, configurable fuzzing, and engineering-productivity environments for fast iteration without production risk.
\end{itemize}
\subsec{AI-Native Product Infrastructure}
\begin{itemize}
  \item Built Gemini-based software-engineering agents, SWE-bench evaluation harnesses, planning-vs-execution metrics, and vector-search benchmarks in Google Cloud Office of the CTO.
  \item Runs a live autonomous-agent fleet with MCP-style tools, reusable skills, workflow routing, tracing, CI gates, human-review controls, and operational recovery.
  \item Built backend, platform, cloud, healthcare, and regulated systems in Python and Java across APIs, data workflows, and operational environments.
\end{itemize}
\input{sections/experience}
\input{sections/publicwork}
\input{sections/skills}
\end{document}
