\input{preamble}
\begin{document}
\input{sections/header}
\titleline{Senior Software Engineer, AI/ML Infrastructure \& Platform \textbar{} Agentic Systems, Tools, and Evals}
\rsection{Summary}
Software engineer focused on production AI infrastructure, agentic workflows, tool/skill abstractions, evaluation systems, and observable platform services. Former Meta and Google engineer who built early Gemini-based software-engineering agents, SWE-bench-style eval harnesses, vector-search benchmarks, and production platform systems. Runs a live autonomous-agent fleet with MCP-style tools, reusable skills, tracing, CI gates, and human-review controls.
\rsection{Selected AI Infrastructure \& Platform Portfolio}
\subsec{Agentic Systems, Tools \& Retrieval}
\begin{itemize}
  \item Built MCP-style capability layers where agents invoke tools, APIs, document workflows, browser actions, and external-system actions through typed, reusable interfaces.
  \item Designed multi-step agent orchestration with stateful task decomposition, retries, failure recovery, tool routing, scheduling, and credential boundaries for real production workflows.
  \item In Google Cloud Office of the CTO, built Gemini-based software-engineering agents, SWE-bench evaluation harnesses, planning-vs-execution metrics, and vector-search benchmarks.
\end{itemize}
\subsec{Reliability, Observability \& Regulated Platform Fit}
\begin{itemize}
  \item Instrumented agent fleets with OpenTelemetry traces, metrics, and logs across tool calls, latency, cost, trajectories, and recovery behavior.
  \item Built backend, cloud, and regulated systems across Google, Meta, Citi, ClearDATA, and Lumeris, with emphasis on privacy, access controls, reliability, and maintainable APIs.
  \item Strongest implementation depth is Python and Java, with AI-assisted TypeScript delivery and experience building platform services, CI gates, and developer tooling.
\end{itemize}
\input{sections/experience}
\input{sections/publicwork}
\input{sections/skills}
\end{document}
