\input{preamble}
\begin{document}
\input{sections/header}
\titleline{Engineering \textbar{} Product Systems, Platform APIs, AI Workflows, and High-Agency Execution}
\rsection{Summary}
High-agency software engineer focused on product-platform systems, developer tooling, AI-enabled workflows, and fast, reliable execution. Former Meta and Google engineer who shipped production commerce, platform, identity, and agent systems. Built early Gemini-based software-engineering agents, SWE-bench-style evaluation harnesses, vector-search benchmarks, and a live autonomous-agent fleet with MCP-style tools, reusable skills, CI gates, and observability.
\rsection{Selected Product \& AI Engineering Portfolio}
\subsec{Product Systems, Marketplaces \& Business Impact}
\begin{itemize}
  \item At Meta Marketplace, expanded third-party partner APIs and shipped-listing workflows, then launched an ML-assisted listing flow that removed manual item-weight entry and lifted new-listing creation about 8\%.
  \item Built systems across consumer marketplaces, regulated healthcare/cloud, enterprise identity, internal IAM, and developer platforms, with strongest implementation depth in Python and Java.
  \item Comfortable moving across backend APIs, product workflows, automation, platform reliability, and AI-assisted TypeScript delivery when the business problem calls for it.
\end{itemize}
\subsec{AI-Enabled Engineering \& Developer Leverage}
\begin{itemize}
  \item In Google Cloud Office of the CTO, built Gemini-based software-engineering agents, SWE-bench evaluation harnesses, planning-vs-execution metrics, and vector-search benchmarks.
  \item Runs a live autonomous-agent fleet with MCP-style tools, reusable skills, OpenTelemetry traces, CI-backed verification, and long-running credentialed workflows.
  \item Uses AI tools as modern engineering leverage while preserving tests, review, source-grounding, and human-control boundaries for production work.
\end{itemize}
\input{sections/experience}
\input{sections/publicwork}
\input{sections/skills}
\end{document}
