\rsection{Experience}

\role{Software Engineer}{Meta}{2025--2026}
\begin{itemize}
  \item Built and operated production systems across Meta product surfaces with product, data, legal, business, partner, and engineering stakeholders.
  \item Led a Facebook Marketplace shipped-listing flow improvement that removed manual package-weight entry by using image-based ML prediction; coordinated with an ML engineer, evaluated predictions against user-entered weights and carrier actuals, met an approximately 80\% accuracy launch threshold, and drove about 8\% uplift in new shipped-listing creation.
  \item Expanded Facebook Marketplace third-party partner APIs and represented Meta with an external partner while coordinating legal, business, product, and engineering requirements.
  \item Built and used agentic developer workflows around code generation, test generation, tool execution, evals, and autonomous engineering loops; strongest recent work centers on agent harnesses, skills/playbooks, and production-style reliability constraints.
\end{itemize}

\role{Software Engineer}{Google}{2018--2025}
\begin{itemize}
  \item Worked across Google Shopping, Google Play, Google Cloud Office of the CTO, and Internal IAM, spanning consumer products, cloud innovation, enterprise identity, and infrastructure.
  \item Built first-wave agentic-coding systems in Google Cloud Office of the CTO, including an early Gemini-based software-engineering agent prototype, SWE-bench evaluation harnesses, planning-vs-execution measurement, target-file precision/recall/F1, and test-pass metrics to guide funding and staffing decisions.
  \item Built and supported large-scale commerce, platform, identity, and infrastructure systems with reliability, security, maintainability, and trust-sensitive workflow constraints.
  \item Built a smoke-test framework for Google Play third-party offerings on a two-person senior-engineer team and contributed to Google Play engagement work including shared leaderboard experiences.
  \item Worked on Insider Risk systems related to internal security, risk, enterprise identity, and trust-sensitive access workflows.
\end{itemize}

\role{Earlier Software Engineering Roles}{Citi, Lumeris, ClearDATA, and others}{Pre-2018}
\begin{itemize}
  \item Built backend, platform, cloud, and healthcare technology systems across Python, Java, backend services, APIs, data workflows, identity systems, and regulated environments.
\end{itemize}
